### 2019-09-17 Thesis/promonads.tex
The final commit?

\begin{theorem}[\cite{RepresentableMulticategories}]
  \label{TheRepresentableMulticategories}
  Let $\M$ be a multicategory and suppose that for each natural number $n$ and each sequence $a_1,\cdots,a_n$ of objects of $\M$ there is an object $\tensor \vec{a}$ and a multimorphism
  \[
    \pi_{\vec a} \from a_1,\cdots,a_n \to \tensor \vec a\,.
    \]
  Suppose that the $\pi_{\vec a}$ are \emph{strongly universal} in the sense that if $b_1,\cdots b_k, c_1,\cdots,c_l$ are two (possibly empty) lists of objects, and $d$ is an object, then any multimorphism
  \[
    f \from b_1,\cdots,b_k,a_1,\cdots,a_n,c_1,\cdots,c_l \to d
    \]
  factors uniquely through $\pi_{\vec a}$; i.e., there is a unique morphism
  \[
    \hat{f} \from b_1,\cdots,b_k,\tensor\vec{a},c_1,\cdots,c_l \to d
    \]
  such that
  \[
    f=(\id_{b_1},\cdots,\id_{b_k},\pi_{\vec a},\id_{c_1},\cdots,\id_{c_l});\hat{f}\,.
    \]
  Given objects $a,b$ of $\M$, define $a\tensor b = \tensor a,b$, and let $I$ be the object $\tensor\epsilon$, where $\epsilon$ is the empty list.  
  Then the operation $\blank\tensor\blank$ and $I$ give rise to the multicategory structure on $\M$:
  \begin{itemize}
    \item $\blank\tensor\blank$ and $I$ are the monoidal product and unit of a monoidal category on $\M_1$, the underlying category of $\M$.
    \item For any sequence $a_1,\cdots a_n$ of objects of $\M$ there is a canonical isomorphism
      \[
        a_1 \tensor \cdots \tensor a_n \cong \tensor \vec a\,,
        \]
      for any bracketing of the left hand side, and the associators and unitors in $\M_1$ are induced from these isomorphisms.
    \item The set of multimorphisms $a_1,\cdots,a_n \to b$ is in bijection with the set of morphisms $a_1\tensor\cdots\tensor a_n \to b$ for $n\ge1$, and the set of multimorphisms $\to b$ is in bijection with the set of morphisms $I \to b$, and these bijections commute with the multicategory composition in $\M$ and the composition in $\M_1$.
  \end{itemize}
\end{theorem}

@@

\begin{definition}
  Let $\M,\N$ be multicategories, where $\M$ is symmetric.  
  Then the collection of multifunctors $\M\to\N$ forms a multicategory.  
  A multimorphism $F_1,\cdots,F_n\Rightarrow G$, where $F_1,\cdots,F_n,G$ are multifunctors $\M\to \N$, is given by a family
  \[
    \phi_a \from F_1(a),\cdots,F_n(a) \to G(a)
    \]
  such that for any multimorphism $f\from a_1,\cdots,a_m\to b$ in $\M$, the diagram
  \[
    \begin{tikzcd}[column sep=46pt]
      F_1(a_1),\cdots,F_n(a_1),\cdots,F_1(a_m),\cdots,F_n(a_m) \arrow[r, "{\phi_{a_1},\cdots,\phi_{a_m}}"] \arrow[d, "\sigma_*"']
        & G(a_1),\cdots,G(a_m) \arrow[dd, "Gf"] \\
      F_1(a_1),\cdots,F_1(a_m),\cdots,F_n(a_1),\cdots,F_n(a_m) \arrow[d, "{F_1f,\cdots,F_nf}"']
        & \\
      F_1(b),\cdots,F_n(b) \arrow[r, "\phi_b"]
        & G(b)
    \end{tikzcd}
    \]
  commutes, where $\sigma$ is the map
  \begin{mathpar}
    \{(1,1),\cdots,(n,1),\cdots,(1,m),\cdots,(n,m)\} \to \{(1,1),\cdots,(1,m),\cdots,(n,1),\cdots,(n,m)\}
  \end{mathpar}
  that sends $(i,j)$ to $(j,i)$, considered as a permutation of $\{1,\cdots,mn\}$.
\end{definition}

@@

Suppose that $\V$ is the category of sets, so that the multimorphisms
\[
  F_1,\cdots,F_n \to G
  \]
are ordinary extranatural transformations
\[
  \phi_{a,\vec{b},c} \from F_1(a,b_1),\cdots,F_n(b_{n-1},c) \to G(a,c)\,.
  \]
Then the definition of the \emph{coend}
\[
  \int_{b_1,\cdots,b_{n-1}\from\C} F_1(a,b_1)\times\cdots\times F_n(b_{n-1},c)
  \]
is that it is universal among all objects admitting such an extranatural transformation out of them.  
It follows that in this case (and more generally, if $\V$ is a cocomplete monoidal category), that the multicategory of endoprofunctors on $\C$ is representable, with monoidal product given by
\[
  F\tensor G(a, c) = \int_{b\from \C} F(a,b) \times G(b,c)\,.
  \]
This is the usual notion of composition for $\Set$-enriched profunctors.  
However, if $\V$ is not cocomplete, then the multicategory of endoprofunctors on $\C$ need not be representable, even if $\V$ is representable.

We have only considered profunctors going from a category into itself.  
Profunctors in general form a structure called an \emph{fc-multicategory} \cite{Multicategories}, though we shall not be using this notion.

@@

Let $\X$ be a monoidal category and let $\M$ be a multicategory.
We define a multicategory $[\X,\M]$ where the objects are ordinary functors
\[
  \X \to \M_1
  \]
and where multimorphisms $F_1,\cdots,F_n\to G$ are natural transformations
\[
  \phi_{x_1,\cdots,x_n} \from F_1(x_1),\cdots,F_n(x_n)\to G(x_1\tensor\cdots\tensor x_n)\,.
  \]
\begin{remark}
  Suppose that $\M$ is the category of sets, regarded as a multicategory through its Cartesian structure.  
  Let $x_1,\cdots,x_n,y_1,\cdots,y_p$ be objects of $\X$.  
  Then for any collection of functors
  \[
    F_1,\cdots,F_n,G_1,\cdots,G_p,H \from \X \to \Set\,,
    \]
  the set of natural transformations
  \[
    \phi_{\vec{x},\vec{y}} \from \prod_i F_i(x_i) \times \prod_j G_j(y_j) \to H(x_1\tensor\cdots\tensor x_n\tensor y_1\tensor\cdots\tensor y_p)
    \]
  may be written as the end
  \[
    \int_{\vec{x},\vec{y}} \left[\prod_i F_i(x_i) \times \prod_j G_j(y_j) ,  H\left(\Tensor_i x_i \tensor \Tensor_j y_j\right)\right]\,.
    \]
  We may then perform some co/end calculus (See the similar computation in \cite{Pisani}, but note that that version is not quite sufficient to prove representability according to Theorem \ref{TheRepresentableMulticategories}).
  \begin{IEEEeqnarray*}{Cl}
    &\int_{\vec{x},\vec{y}} \left[\prod_i F_i(x_i) \times \prod_j G_j(y_j) ,  H\left(\Tensor_i x_i \tensor \Tensor_j y_j\right)\right]\\
    \cong&\int_{\vec{x},z,\vec{y}} \left[\X\left(\Tensor_i x_i,z\right),\left[\prod_i F_i(x_i) \times \prod_j G_j(y_j) ,  H\left(z \tensor \Tensor_j y_j\right)\right]\right]\\
    \cong&\int_{\vec{x},z,\vec{y}} \left[\prod_i F_i(x_i) \times \X\left(\Tensor_i x_i,z\right) \times \prod_j G_j(y_j),H\left(z \tensor \Tensor_j y_j\right)\right]\\
    \cong&\int_{z,\vec{y}}\left[\int^{\vec{x}} \left(\prod_i F_i(x_i) \times \X\left(\Tensor_i x_i,z\right)\right)\times\prod_j G_j(y_j),H\left(z\tensor\Tensor_j y_j\right)\right]
  \end{IEEEeqnarray*}
  In other words, this multicategory is representable by the Day convolution that we met in Definition \ref{DefDayConvolution}:
  \[
    (F\tensor_{\text{Day}} G)(z) = \int^{x,y} F(x) \times G(y)\times \X(x\tensor y,z)\,.
    \]
  However, this multicategory is not representable in general, particularly in the cases when we are working with enriched multicategories (not defined here), where the enriching multicategory is not cocomplete, or when the category $\M$ is not the enriching category.
\end{remark}

@@

This generalizes categories in the case that $\X=1$.  
It generalizes monoidal functors $\X \to \Set$ in the case that $\C$ is the enriched category $*_{[\X,\Set]}$ with a single object $()$, where the morphisms $() \to ()$ are given by the functor $[I,\blank]$, for $I$ the monoidal unit in $\X$, this being the initial object in $[\X,\Set]$.

@@

The objects of this $[\X,\Set]$-enriched category are the objects of $\C$.
By working the definitions through the proofs of Proposition \ref{PropFunctorsIntoProfunctors} and Theorem \ref{StokessTheorem}, we see that the object of morphisms from $a$ to $b$ is
\[
  x \mapsto \C(a,x.b)\,,
  \]
and that composition of morphisms is the multimorphism
\[
  \C(a,x.b) \times \C(b,y.c) \to \C(a,(x\tensor y).c)
  \]
in $[\X,\Set]$ given by sending morphisms $f\from a \to x.b$, $g\from b \to x.c$ to the composite
\[
  a
  \xrightarrow{f}
  x.b
  \xrightarrow{x.g}
  x.y.c \xrightarrow{m}
  (x\tensor y).c\,,
  \]
which is precisely the definition of composition in the \Mellies category.

>>>>

\begin{theorem}[\cite{RepresentableMulticategories}]
  \label{TheRepresentableMulticategories}
  Let $\M$ be a multicategory and suppose that for each natural number $n$ and each sequence $a_1,\cdots,a_n$ of objects of $\M$ there is an object $\tensor \vec{a}$ and a multimorphism
  \[
    \pi_{\vec a} \from a_1,\cdots,a_n \to \tensor \vec a\,.
    \]
  Suppose that the $\pi_{\vec a}$ are \emph{strongly universal} in the sense that if 
  \begin{mathpar}
    b_1,\cdots b_k, c_1
    \and
    \cdots,c_l
  \end{mathpar}
  are two (possibly empty) lists of objects, and $d$ is an object, then any multimorphism
  \[
    f \from b_1,\cdots,b_k,a_1,\cdots,a_n,c_1,\cdots,c_l \to d
    \]
  factors uniquely through $\pi_{\vec a}$; i.e., there is a unique morphism
  \[
    \hat{f} \from b_1,\cdots,b_k,\tensor\vec{a},c_1,\cdots,c_l \to d
    \]
  such that
  \[
    f=(\id_{b_1},\cdots,\id_{b_k},\pi_{\vec a},\id_{c_1},\cdots,\id_{c_l});\hat{f}\,.
    \]
  Given objects $a,b$ of $\M$, define $a\tensor b = \tensor a,b$, and let $I$ be the object $\tensor\epsilon$, where $\epsilon$ is the empty list.  
  Then the operation $\blank\tensor\blank$ and $I$ make $\M$ into a monoidal category $\overline{\M}$ such that $\tilde{\overline{\M}}$ and $\M$ are isomorphic multicategories.
  \begin{itemize}
    \item $\blank\tensor\blank$ and $I$ are the monoidal product and unit of a monoidal category on $\M_1$, the underlying category of $\M$.
    \item For any sequence $a_1,\cdots a_n$ of objects of $\M$ there is a canonical isomorphism
      \[
        a_1 \tensor \cdots \tensor a_n \cong \tensor \vec a\,,
        \]
      for any bracketing of the left hand side, and the associators and unitors in $\M_1$ are induced from these isomorphisms.
    \item The set of multimorphisms $a_1,\cdots,a_n \to b$ is in bijection with the set of morphisms $a_1\tensor\cdots\tensor a_n \to b$ for $n\ge1$, and the set of multimorphisms $\to b$ is in bijection with the set of morphisms $I \to b$, and these bijections commute with the multicategory composition in $\M$ and the composition in $\M_1$.
  \end{itemize}
\end{theorem}

@@

\begin{definition}
  Let $\M,\N$ be multicategories, where $\M$ is symmetric.  
  Then the collection of multifunctors $\M\to\N$ forms a multicategory.  
  A multimorphism $F_1,\cdots,F_n\Rightarrow G$, where $F_1,\cdots,F_n,G$ are multifunctors $\M\to \N$, is given by a family
  \[
    \phi_a \from F_1(a),\cdots,F_n(a) \to G(a)
    \]
  such that for any multimorphism $f\from a_1,\cdots,a_m\to b$ in $\M$, the diagram
  \[
    \begin{tikzcd}[column sep=46pt]
      F_1(a_1),\cdots,F_n(a_1),\cdots,F_1(a_m),\cdots,F_n(a_m) \arrow[r, "{\phi_{a_1},\cdots,\phi_{a_m}}"] \arrow[d, "\sigma_*"']
        & G(a_1),\cdots,G(a_m) \arrow[dd, "Gf"] \\
      F_1(a_1),\cdots,F_1(a_m),\cdots,F_n(a_1),\cdots,F_n(a_m) \arrow[d, "{F_1f,\cdots,F_nf}"']
        & \\
      F_1(b),\cdots,F_n(b) \arrow[r, "\phi_b"]
        & G(b)
    \end{tikzcd}
    \]
  commutes, where $\sigma$ is the map
  \begin{mathpar}
    (1,1),\cdots,(n,1),\cdots,(1,m),\cdots,(n,m) \to (1,1),\cdots,(1,m),\cdots,(n,1),\cdots,(n,m)
  \end{mathpar}
  sending $(i,j)$ to $(i,j)$, considered as a permutation of $\{1,\cdots,mn\}$.
\end{definition}

@@

Suppose that $\V$ is the category of sets, so that the multimorphisms
\[
  F_1,\cdots,F_n \to G
  \]
are ordinary extranatural transformations
\[
  \phi_{a,\vec{b},c} \from F_1(a,b_1),\cdots,F_n(b_{n-1},c) \to G(a,c)\,.
  \]
Then the definition of the \emph{coend}
\[
  \int_{b_1,\cdots,b_{n-1}\from\C} F_1(a,b_1)\times\cdots\times F_n(b_{n-1},c)
  \]
is that it is universal among all objects admitting such an extranatural transformation out of them.  
It follows that in this case (and more generally, if $\V$ is a cocomplete monoidal category), that the multicategory of endoprofunctors on $\C$ is representable, with monoidal product given by
\[
  F\tensor G(a, c) = \int_{b\from \C} F(a,b) \times G(b,c)\,.
  \]
This is the usual notion of composition for $\Set$-enriched profunctors.  
However, it relies on the appropriate coends existing in $\Set$; for more generally $\V$-enriched profunctors, the multicategory of endoprofunctors on $\C$ need not be representable, even if $\V$ is a monoidal category.

We have only considered profunctors going from a category into itself.  
Profunctors in general form a structure called an \emph{fc-multicategory} \cite{Multicategories}, but we shall not be using this notion.

@@

Let $\X$ be a monoidal category and let $\M$ be a multicategory.
We define a multicategory $[\X,\M]$ where the objects are ordinary functors
\[
  \X \to \M_1
  \]
and where multimorphisms $F_1,\cdots,F_n\to G$ are natural transformations
\[
  \phi_{x_1,\cdots,x_n} \from F_1(x_1),\cdots,F_n(x_n)\to G(x_1\tensor\cdots\tensor x_n)\,.
  \]
\begin{remark}
  Suppose that $\M$ is the category of sets, regarded as a multicategory through its Cartesian structure.  
  Let $x_1,\cdots,x_n,y_1,\cdots,y_p$ be objects of $\X$.  
  Then for any collection of functors
  \[
    F_1,\cdots,F_n,G_1,\cdots,G_p,H \from \X \to \Set\,,
    \]
  the set of natural transformations
  \[
    \phi_{\vec{x},\vec{y}} \from \prod_i F_i(x_i) \times \prod_j G_j(y_j) \to H(x_1\tensor\cdots\tensor x_n\tensor y_1\tensor\cdots\tensor y_p)
    \]
  may be written as the end
  \[
    \int_{\vec{x},\vec{y}} \left[\prod_i F_i(x_i) \times \prod_j G_j(y_j) ,  H\left(\Tensor_i x_i \tensor \Tensor_j y_j\right)\right]\,.
    \]
  We may then perform some co/end calculus (See the similar computation in \cite{Pisani}, but note that that version is not quite sufficient to prove representability according to Theorem \ref{TheRepresentableMulticategories}).
  \begin{IEEEeqnarray*}{Cl}
    &\int_{\vec{x},\vec{y}} \left[\prod_i F_i(x_i) \times \prod_j G_j(y_j) ,  H\left(\Tensor_i x_i \tensor \Tensor_j y_j\right)\right]\\
    \cong&\int_{\vec{x},z,\vec{y}} \left[\X\left(\Tensor_i x_i,z\right),\left[\prod_i F_i(x_i) \times \prod_j G_j(y_j) ,  H\left(z \tensor \Tensor_j y_j\right)\right]\right]\\
    \cong&\int_{\vec{x},z,\vec{y}} \left[\prod_i F_i(x_i) \times \X\left(\Tensor_i x_i,z\right) \times \prod_j G_j(y_j),H\left(z \tensor \Tensor_j y_j\right)\right]\\
    \cong&\int_{z,\vec{y}}\left[\int^{\vec{x}} \left(\prod_i F_i(x_i) \times \X\left(\Tensor_i x_i,z\right)\right)\times\prod_j G_j(y_j),H\left(z\tensor\Tensor_j y_j\right)\right]
  \end{IEEEeqnarray*}
  In other words, this multicategory is representable by the Day convolution that we met in Definition \ref{DefDayConvolution}:
  \[
    (F\tensor_{\text{Day}} G)(z) = \int^{x,y} F(x) \times G(y)\times \X(x\tensor y,z)\,.
    \]
  However, this multicategory is not representable in general, particularly in the cases when we are working with enriched multicategories (not defined here), where the enriching multicategory is not cocomplete, or when the category $\M$ is not the enriching multicategory.
\end{remark}

@@

This generalizes categories in the case that $\X=1$.  
It generalizes monoidal functors $\X \to \Set$ in the case that $\C$ is the $[\X,\Set]$-enriched category $*_{[\X,\Set]}$ with a single object $()$, where the morphisms $() \to ()$ are given by the functor $[I,\blank]$, for $I$ the monoidal unit in $\X$, this being the initial object in $[\X,\Set]$.

@@

The objects of this $[\X,\Set]$-enriched category are the objects of $\C$.
By working the definitions through the proofs of Proposition \ref{PropFunctorsIntoProfunctors} and Theorem \ref{StokessTheorem}, we see that the object of morphisms from $a$ to $b$ is the functor
\[
  x \mapsto \C(a,x.b)\from \X \to \Set\,,
  \]
and that composition of morphisms is the multimorphism
\[
  \C(a,x.b) \times \C(b,y.c) \to \C(a,(x\tensor y).c)
  \]
in $[\X,\Set]$ given by sending morphisms $f\from a \to x.b$, $g\from b \to x.c$ to the composite
\[
  a
  \xrightarrow{f}
  x.b
  \xrightarrow{x.g}
  x.y.c \xrightarrow{m}
  (x\tensor y).c\,,
  \]
which is precisely the definition of composition in the \Mellies category.
